---
title: "Coursera - Data Products"
author: "Andre"
date: "4 april 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dslabs)
library(tidyverse)
data("murders")
```

## Motivation - Gun murder data

When choosing a place to live the security can be an important feature.

To help the decision I created an way to better visualize this information using Shiny.

## Data

The data for this report came from the FBI througth the R package *dslabs* and have the following summary.

```{r summary}
summary(murders)
```

## Visualizing the data

To understand the data first we can see a plot with each country, his population and total gun murders in 2010. 

```{r plot}
qplot(data = murders, x = population, y = total) + stat_smooth(method = "lm") + ylab('Total gun murders in 2010') + xlab('Population')
```

## Detailing the data

To understand even better we can see not only the total of murders, but also the top 5 states with highest murder rate, since the total number can be misleading.

We can also filter by region of the U.S.

```{r table}
murders %>% mutate(murder_rate_per_100000 = total/population*100000) %>% select(region, state, murder_rate_per_100000, gun_murders = total, population) %>% arrange(desc(murder_rate_per_100000)) %>% top_n(5)
```
